---
title: "Cherigny - gradeslab"
author: "Adèle Cherigny"
format: html
---

# 1-Introduction
## 1.1- Study organisation
## 1.2- Data set
### Question 1: Load the data set
Chargement des packages nécessaires: 
```{r}
library(readr)
```

Chargement de la base de données
```{r}
here::i_am("grades-lab.Rproj")
library(here)
grades <- read_csv(here("grades.csv"))
```


# 2-Simple analysis
### Question 2:
The data set contains `r nrow(grades)` grades.

### Question 3: 
chargement des packages nécessaires:
```{r}
library(dplyr)
```
There `r nrow(grades %>% distinct(id))` students in the data set.

### Question 4: 
```{r}
grades%>%
  select(id, group)%>%
  distinct(id, .keep_all = TRUE)%>%
  slice_sample(n =5)%>%
  knitr::kable()
```
### Question 5:
chargement des packages nécessaires:
```{r}
library(ggplot2)
```

```{r}
grades%>%
  select(id, group)%>%
  distinct(id, .keep_all = TRUE)%>%
  mutate(group = factor(group)) %>%
  ggplot(aes(x= group))+
  geom_bar(show.legend = TRUE)+
  labs(x = "Groups", y = "Number of students")
```
 
### QUestion 6: 
```{r}
grades %>%
  group_by(group, course)%>%
  filter(course== "Architecture and Sculpture")%>%
  summarise(average =mean(grade))%>%
  select (-course)%>% 
  mutate(group = factor(group)) %>%
  ggplot(aes(x= group, y= average, fill = group))+
  geom_col()+
  labs(x = "Groups", y = "average in Architecture and Sculpture")
```

### Question 7:
```{r}
grades%>%
  group_by(module)%>%
  summarise(average= mean(grade))%>%
  mutate(module = factor(module)) %>%
  ggplot(aes (x = module, y = average, fill =module))+
  geom_col()
```

